Matching Bullets

### 2015-11-29 imaging-paper.Rnw
matching land D-5

\begin{figure}
\begin{subfigure}[t]{.49\textwidth}
\caption{Maximal number of CMS between Bullet land and all of the 120 other (known) lands. For two lands the number of maximum CMS is high. }
<<cms, echo=FALSE, fig.width=5, fig.height=3, out.width='\\textwidth'>>=
load("data/unkn17.RData")
cmsdist <- sapply(reslist, function(x) x$maxCMS)

qplot(cmsdist, geom="bar") + theme_bw() + xlab("Number of CMS")
@
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}
\caption{Overlaid lines of the land of the unknown bullet and the land with the top matching CMS.}
<<top, echo=FALSE, fig.width=5, fig.height=3, out.width='\\textwidth'>>=
res <- reslist[[which.max(cmsdist)]]  
#res <- reslist[[which.max(cmsdist[-which.max(cmsdist)])]]  # number 2

@@

\caption{Overlaid lines of the land of the unknown bullet and the land with the second top matching CMS.}
<<top2, echo=FALSE, fig.width=5, fig.height=3, out.width='\\textwidth'>>=
#res <- reslist[[which.max(cmsdist)]]  
res <- reslist[[which.max(cmsdist[-which.max(cmsdist)])]]  # number 2

@@

@
\end{subfigure}
\end{figure}

>>>>

\begin{figure}
\begin{subfigure}[t]{.49\textwidth}
\caption{Maximal number of CMS between unknown Bullet D land 5 and all of the 120 other (known) lands. For two lands the number of maximum CMS is high. }
<<cms, echo=FALSE, fig.width=7, fig.height=3.5, out.width='\\textwidth'>>=
load("data/unkn17.RData")
cmsdist <- sapply(reslist, function(x) x$maxCMS)

qplot(cmsdist, geom="bar") + theme_bw() + xlab("Number of CMS")
@
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}
\caption{Overlaid lines of the land of the unknown bullet D-5 and the land with the top matching CMS.}
<<top, echo=FALSE, fig.width=7, fig.height=3.5, out.width='\\textwidth', warning = FALSE>>=
res <- reslist[[which.max(cmsdist)]]  
#res <- reslist[[which.max(cmsdist[-which.max(cmsdist)])]]  # number 2

@@

\caption{Overlaid lines of the land of the unknown bullet D-5 and the land with the second top matching CMS.}
<<top2, echo=FALSE, fig.width=7, fig.height=3.5, out.width='\\textwidth', warning = FALSE>>=
#res <- reslist[[which.max(cmsdist)]]  
res <- reslist[[which.max(cmsdist[-which.max(cmsdist)])]]  # number 2

@@

@
\end{subfigure}
\caption{\label{fig:hamby-perfect}Showcase scenario of when matching with CMS works perfectly. Unfortunately the matches are not always that convincing.}
\end{figure}
